Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-25 presentacion_hiram/presentacion-tesis.tex
n

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{\tiny
			L.F. Hiram Ernesto Dami\'an\\
			\vspace{5px}
				Director:\\
					\vspace{5px}
			Jos\'e Feliciano Ben\'itez Rubio\\
				\vspace{5px}
				Maestr\'ia en Ciencias (F\'isica)\\
					\vspace{5px}
			 Departamento de Investigacion en F\'isica }
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	\date{\small November 15$^{th}$ 2019}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
\hline 	
Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
\hline 
Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
\hline 	
Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
\hline 
Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
\hline 
Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
\hline 
Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
\hline 
Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
\hline 
$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
\hline 
$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
\hline
Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
\hline 
Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
\hline 
Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
\hline 
Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
\hline 
$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\end{frame}

@@

\begin{itemize}
	\item $\Phi$ is higgs field which is a complex scalar field. $\Phi$
	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
	%\item g and g are boson coupling constants.
	\item $\lambda $ and $\mu^2$ are Higgs potential parameters
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SM Lagrangian}
Yukawa lagrangian
\begin{align}
\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}%+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
\end{align}
\scriptsize{where h.c is hermitian conjugate. m and n are flavors of quarks and leptons.
\\
The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
Choosing}
\begin{align*}
\Phi=-\frac{1}{2}\left(\begin{array}{c}
0 \\
v+h
\end{array} \right) \label{vmin}
\end{align*}
\scriptsize{
By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
\begin{align*}
\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
\end{align*}
from which the masses for the fermions shown to be proportional to the Yukawa couplings
\begin{align*}
m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
\end{align*}}
\end{frame}

@@

%\begin{frame}
%\section{Supportive slides}
%\huge{Back up}
%\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{\tiny
			L.F. Hiram Ernesto Dami\'an\\
			\vspace{5px}
				Director:\\
					\vspace{5px}
			Jos\'e Feliciano Ben\'itez Rubio\\
				\vspace{5px}
				Maestr\'ia en Ciencias (F\'isica)\\
					\vspace{5px}
			 Departamento de Investigacion en F\'isica }
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	\date{\small November 25$^{th}$ 2019}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
\hline 	
Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
\hline 
Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
\hline 	
Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
\hline 
Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
\hline 
Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
\hline 
Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
\hline 
Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
\hline 
$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
\hline 
$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
\hline
Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
\hline 
Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
\hline 
Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
\hline 
Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
\hline 
$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at $v$=0.998c}
\end{frame}

@@

\begin{itemize}
	\item $\Phi$ is Higgs field which is a complex scalar field. $\Phi$
	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
	%\item g and g are boson coupling constants.
	\item $\lambda $ and $\mu^2$ are Higgs potential parameters
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Electroweak SM Lagrangian}
	\begin{figure}[ht!]
		\centering
		\begin{tikzpicture}[scale=1.2]
		\begin{axis}[
		hide axis,
		%axis lines=middle,
		%      axis on top,
		%      axis line style={blue,dashed,thick},
		%      ymin=-2,ymax=2,
		%      xmin=-2,xmax=2,
		%      zmin=-2,zmax=2,
		samples=30,
		domain=0:360,
		y domain=0:1.25,clip=false
		]
		\addplot3 [surf, shader=flat, draw=black, fill=white, z buffer=sort]
		({sin(x)*y}, {cos(x)*y}, {(y^2-1)^2});
		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:1,0,0)
		node[below,font=\footnotesize]{$\Phi_{\text{IM}}$};
		\draw[blue,thick,-stealth] (axis cs:1,0,0) -- (axis cs:1.3,0,0)
		node[above,font=\footnotesize]{};
		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,-1,0)
		node[left=2mm,font=\footnotesize]{$\Phi_{\text{RE}}$};
		\draw[blue,thick,-stealth] (axis cs:0,-1,0) -- (axis cs:0,-1.5,0)
		node[right=1mm,font=\footnotesize]{};
		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,0,1)
		%node[left=2mm,font=\footnotesize]{$\phi_{\text{RE}}$}
		;
		\draw[blue,thick,-stealth] (axis cs:0,0,1) -- (axis cs:0,0,1.3)
		node[right,font=\footnotesize]{$V(\Phi)$};
		\end{axis}
		\end{tikzpicture}
		\caption*{\small Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$, also called the mexican hat potential.}
		\label{hat}
	\end{figure}
\end{frame}
\begin{frame}
\frametitle{SM Lagrangian}
Yukawa lagrangian
\begin{align}
\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}%+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
\end{align}
\scriptsize{where h.c is hermitian conjugate. m and n are flavors of quarks and leptons.
\\
The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
Choosing}
\begin{align*}
\Phi=-\frac{1}{2}\left(\begin{array}{c}
0 \\
v+h
\end{array} \right) \label{vmin}
\end{align*}
\scriptsize{
By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
\begin{align*}
\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
\end{align*}
from which the masses for the fermions shown to be proportional to the Yukawa couplings
\begin{align*}
m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
\end{align*}}
\end{frame}

@@

\begin{frame}
\section{Supportive slides}
\huge{Back up}
\end{frame}
